An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-12-31 EconGrowth2.Rnw
Now correctly referring to China for zoomed spaghetti graph.

Figure~\ref{fig:CES_Spaghetti_Graph_ZM} shows details of the resample fits for Zambia with the (kl)e nesting.

<<CES_Spaghetti_Graph_ZM, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models for Zambia with the (kl)e nesting.">>=
cesSpaghettiGraph(data=subset(spagData, Country=="ZM" & nest=="(kl)e"), level=1)
@

>>>>

Figure~\ref{fig:CES_Spaghetti_Graph_CN} shows details of the resample fits for China with the (kl)e nesting.

<<CES_Spaghetti_Graph_CN, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
cesSpaghettiGraph(data=subset(spagData, Country=="CN" & nest=="(kl)e"), level=1)
@
